|

### 2023-05-21 manuscript/paper.Rmd
Update Manuscript

## Completed Data Model 
For each of the $M = 100$ imputed datasets, we fit an OU model for different phenotypes of interest.  We choose one of the columns of $X$ to be the target phenotype and our analysis is repeated for all phenotypes of interest.

Let $W_{ti}$, $\boldsymbol{X}_{ti}$, and $\boldsymbol{Y}_{ti}$ be the imputed gender, $K_{cont} \times 1$ vector of continuous phenotypes, and $K_{disc} \times 1$ vector of discrete phenotypes, respectively, for the $i$-th observed fossil in year $t$ for $t = 1, \ldots, 18$ and  $i = 1\ldots,n_{t}$.  In addition,

>>>>

## Completed Data Model 
For each of the $M = 100$ imputed datasets, we fit an OU model for different phenotypes of interest.  For the $i$-th observed fossil in year $t$ ($t = 1, \ldots, 18$ and  $i = 1\ldots,n_{t}$), let $W_{ti}$ be the imputed gender, $\boldsymbol{X}_{ti}$ be the $K_{cont} \times 1$ vector of continuous phenotypes, and $\boldsymbol{Y}_{ti}$ be the $K_{disc} \times 1$ vector of discrete phenotypes for.  In addition,
